---
title: "Cultural Dynamics and Global Media Consumption in Taiwan"
subtitle: "An Empirical Analysis of the 2018 Taiwan Social Change Survey"
author: "Richie Peng"
output:
  github_document: default
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

load("dataset.rda")
library(dplyr)
library(ggplot2)
library(visreg)
load("dataset.rda")

dataset$a1 <- factor(dataset$a1)
levels(dataset$a1) <- c("Male", "Female")

temp_age <- ifelse(dataset$a2n >= 97, NA, dataset$a2n) 
temp_age <- dplyr::recode(unclass(temp_age),
            '1'=18.5, '2'=24.5, '3'=34.5, '4'=44.5, 
            '5'=54.5, '6'=64.5, '7'=74.5, '8'=80) 
dataset$Age <- temp_age 

temp_inc <- ifelse(dataset$h28 >= 92, NA, dataset$h28)
temp_inc <- dplyr::recode(unclass(temp_inc), 
            '1'=0, '2'=0.5, '3'=1.5, '4'=2.5, '5'=3.5, 
            '6'=4.5, '7'=5.5, '8'=6.5, '9'=7.5, '10'=8.5, 
            '11'=9.5, '12'=10.5, '13'=11.5, '14'=12.5, '15'=13.5, 
            '16'=14.5, '17'=15.5, '18'=16.5, '19'=17.5, '20'=18.5, 
            '21'=19.5, '22'=25, '23'=35, '24'=45, '25'=75, '26'=100)
dataset$Income <- temp_inc

dataset$a6 <- factor(dataset$a6) 
levels(dataset$a6) <- c("Metropolis", "Suburbs", "Cities", "Villages", "Farmhouses", NA, NA, NA, NA)
```

# 1. Introduction

## Background
Taiwanese society exhibits a unique co-existence of rich traditional Chinese cultural roots and rapid integration into Western globalization. As modernization accelerates, individuals are increasingly exposed to foreign lifestyles, western dietary habits, and international travel. Understanding how these global forces interact with domestic values is a core question in sociology and cultural studies. This project uses empirical data from the **2018 Taiwan Social Change Survey** to quantitatively evaluate how Taiwanese cultural preferences and media consumption are shaped by personal socio-demographic backgrounds and lifestyle choices.

## Purpose
The primary purpose of this project is to analyze the factors influencing two key aspects of cultural dynamics in Taiwan:
1. **Traditional Cultural Appreciation**: The perceived importance of traditional Chinese history and culture.
2. **Western Media Consumption**: The habit of watching Western movies.

By utilizing **logistic regression** modeling, we examine whether a "digital and cultural divide" exists across age, gender, income levels, and urbanization types, and investigate whether lifestyle proxies (like eating European food or international travel) drive shifts in cultural values.

## Goals
* Build and interpret multiple binary **logistic regression** models using the `glm()` function in R to analyze binary outcomes of cultural preferences.
* Evaluate the impact of demographic factors (Age, Gender, Income, and Urbanization) on traditional and globalized preferences.
* Examine the behavioral effects of Western dietary habits and international tourism as external factors of attitude shifts.
* Use `ggplot2` and `visreg` to create professional visualizations that illustrate the predictive probabilities and demographic trends of cultural consumption.

## Techs and Skills
* **Programming Language**: R
* **Libraries Used**: `dplyr` (data wrangling), `ggplot2` (advanced data visualization), `visreg` (regression visualization)
* **Statistical Methods**: Binary **logistic regression** modeling (`glm` with `binomial` family and `logit` link), demographic control analysis, and hypothesis testing.

---

# 2. TL;DR

## Basic Information
* **Dataset**: 2018 Taiwan Social Change Survey
* **Methodology**: Two primary investigations modeled via binary **logistic regression** to estimate log-odds and predictive probabilities of cultural attitudes and consumption.

## Key takeaways
* **Traditional Chinese History and Culture Appreciation**:
  * Demographics play a significant role. **Female** respondents (Estimate = -0.2938, `p-value` = 0.0255) and individuals with **higher income** (Estimate = -0.0244, `p-value` = 0.0133) are significantly less likely to agree with the importance of traditional Chinese culture.
  * Western food consumption (eating European food) was tested as a potential lifestyle cause, but it does **not** have a statistically significant effect on cultural appreciation (Estimate of `EUfoodNever` = 0.1046, `p-value` = 0.4707) when controlling for age and gender.
* **Western Movies Consumption**:
  * A stark demographic and cultural divide is evident. **Younger** (Estimate = -0.0358, `p-value` < 0.001) and **wealthier** (Estimate = 0.0284, `p-value` < 0.001) individuals, as well as **males** (Female Estimate = -0.4454, `p-value` < 0.001), are significantly more likely to watch Western movies.
  * Urbanization presents a clear divide: residents in **Cities** (Estimate = -0.6956, `p-value` < 0.001) and **Villages** (Estimate = -1.0790, `p-value` < 0.001) consume significantly less Western media compared to those living in the **Metropolis** reference group.
  * **International Tourism** is a powerful behavioral driver. Having traveled abroad significantly increases the log-odds of watching Western movies (Estimate of `TourismForeign` = 0.4440, `p-value` = 0.0080), even after controlling for age and income.
  
# 3. Appreciation for Traditional Chinese History and Culture

This section investigates whether demographic backgrounds and lifestyle choices correlate with how strongly individuals value traditional Chinese history and culture.

## Q1 - F13c (Chinese history and culture)

## Q1.1 Demographics

Question: Are people with specific demographic backgrounds (Age, Gender, Income) more likely to agree with the importance of Chinese history and culture?

Analysis 1: I used logistic regression (glm) because the dependent variable (Agree vs. Disagree with the importance of Chinese history and culture) is binary. The model analyzes how demographics like Age, Gender, and Income shape this attitude. Based on the results, we can observe whether older generations or individuals with specific income levels place more value on traditional culture. To add on, age shows a marginally positive trend ($p = 0.063$), but is not statistically significant at the 5% level.

```{r}
dataset$f13c_clean <- ifelse(dataset$f13c >= 90, NA, dataset$f13c)
dataset$AgreeChineseCulture <- ifelse(dataset$f13c_clean <= 3, TRUE, FALSE)

m1_demo <- glm(AgreeChineseCulture ~ a1 + Age + Income, 
               data = dataset, 
               family = binomial(link="logit"))
summary(m1_demo)
```

## Q1.2 Potential Causes

Question: Do lifestyle choices and behaviors (e.g., eating European food) influence people's attitudes towards Chinese history and culture?

Analysis 2: Cultural attitudes are often shaped by external exposure. I included "Eating European Food" (C3e) as a proxy for Western lifestyle exposure. I expect that individuals who frequently consume Western food might show lower agreement with the strict preservation of traditional Chinese culture, acting as a potential cause for the attitude shift.


```{r}
dataset$EUfood <- factor(dataset$c3e)
levels(dataset$EUfood) <- c("Ever eat", "Ever eat", "Ever eat", "Never", NA)

m1_causes <- glm(AgreeChineseCulture ~ Age + a1 + EUfood, 
                 data = dataset, 
                 family = binomial(link="logit"))
summary(m1_causes)
```

## Q1.3 Visualization

I support analysis 2 with this visualization.

```{r}
plotdata1 <- dataset[!is.na(dataset$AgreeChineseCulture) & !is.na(dataset$EUfood), ]

ggplot(plotdata1, aes(x = EUfood, fill = AgreeChineseCulture)) +
  geom_bar() +
  scale_fill_manual(values = c("#e15759", "#5eb6b8")) +
  labs(title = "Cultural Attitudes by Western Food Consumption",
       subtitle = "Does eating EU food associate with attitudes toward Chinese Culture?",
       x = "European Food Consumption",
       y = "Number of respondents",
       fill = "Agrees with Chinese Culture",
       caption = "Source: 2018 Taiwan Social Change Survey")
```

This stacked bar graph demonstrates the distribution and absolute count of agreement with Chinese culture segmented by whether the respondent eats European food. It intuitively shows how exposure to foreign dietary cultures correlates with shifts in domestic cultural attitudes.

# 4. Consumption of Western Movies

This section explores the "digital and cultural divide" regarding the consumption of globalized media (Western movies) and examines if international travel broadens media consumption habits.

## Q2 - G3a05 (Western Movies)

## Q2.1 Demographics

Question: How do demographic factors (Income, Age, and Urbanization level) dictate the consumption of Western movies?

Analysis 1:
I converted G3a05 (watching Western movies) into a binary variable. The logistic regression results test for a "digital/cultural divide." It examines whether younger adults living in metropolises with higher disposable income are significantly more likely to consume Western movies compared to rural or older demographics.

```{r}
clean_g3a <- ifelse(dataset$g3a >= 90, NA, dataset$g3a)

dataset$WatchWestern <- ifelse(clean_g3a == 5, TRUE, FALSE)

m2_demo <- glm(WatchWestern ~ Age + Income + a6 + a1, 
               data = dataset, 
               family = binomial(link="logit"))
summary(m2_demo)
```

## Q2.2 Potential Causes

Question: Does traveling abroad influence domestic media consumption habits (like watching Western movies)?

Analysis 2:
Traveling broadens cultural horizons. I incorporated G8a (Tourism behavior) into the model. The analysis tests the hypothesis that individuals who have experienced foreign tourism are more likely to seek out Western media upon returning home, controlling for their income and age.

```{r}
dataset$Tourism <- factor(dataset$g8a)
levels(dataset$Tourism) <- c("Domestic", "Foreign", "Foreign", "Foreign", 
                             "Foreign", "Foreign", "Foreign", "Foreign", 
                             NA, NA, NA, NA)

m2_causes <- glm(WatchWestern ~ Income + Age + Tourism, 
                 data = dataset, 
                 family = binomial(link="logit"))
summary(m2_causes)
```

## Q2.3 Visualization

I support analysis 2 with this visualization.

```{r, warning=FALSE}
visreg(m2_causes, "Age", scale = "response", gg = TRUE) +
  labs(title = "Younger Generations Consume More Western Media",
       subtitle = "Predicted probability holding income and tourism constant",
       x = "Age of Respondent",
       y = "Probability of Watching Western Movies",
       caption = "Source: 2018 Taiwan Social Change Survey")
```

Using the visreg package, this plot isolates the effect of Age on the probability of watching Western movies, holding other variables constant. The regression curve visually confirms how the predicted probability of consuming Western media changes across different age groups.

# 5. Conclusion

This project has successfully utilized **logistic regression** modeling to explore the sociodemographic determinants of cultural preferences in Taiwan. 

First, our investigation into **Traditional Chinese History and Culture Appreciation** revealed that appreciation is strongly linked to fundamental demographics. Interestingly, female and higher-income respondents show lower interest, whereas dietary exposure to Western culture (such as eating European food) does not exert a significant direct effect. 

Second, the exploration of **Western Movies Consumption** highlighted a distinct socio-demographic and regional divide in media consumption. Younger, male, wealthier, and more metropolitan-based respondents are significantly more likely to watch Western movies. Furthermore, we validated the hypothesis that outbound travel acts as a powerful behavioral catalyst; international tourism experience actively drives individuals to consume globalized media, expanding their cultural patterns.

In summary, globalization in Taiwan does not represent a uniform sweep of Western values. Instead, it manifests as a structured **digital and cultural divide**, heavily dictated by demographic backgrounds, urbanization levels, and direct international experiences.